### spocc - Make some maps!

### Load libraries

```{r load}
library(spocc)
library(rCharts)
```

### spocc unifies access to biodiversity data across sources

```{r sources}
out <- occ(query='Accipiter striatus', from='gbif')
out@gbif@data # a data.frame
out@ebird@data # empty
out@gbif@meta #  metadata, your query parameters, time the call executed, etc. 
```

And you can squash together data from sources easily

```{r manysources}
out <- occ(query='Accipiter striatus', from=c('gbif','bison'))
occtodf(out, 'data')
```


### Make a map using Shiny locally (uses rCharts)

Try changing the species names to whatever you like and press **Submit**

Or change the background map, or the color palette. 

```{r shinymap, eval=FALSE}
mapshiny()
```


### Make a map using rCharts

```{r rcharts, eval=FALSE}
spp <- c('Danaus plexippus','Accipiter striatus','Pinus contorta')
dat <- occlist(query=spp, from='gbif', gbifopts=list(georeferenced=TRUE))
dat <- occtodfspp(dat, 'data')
maprcharts(data=dat)
```


### Make a map using GitHub gists

If you have a Github Account, you can get an interactive map on Github in one line of code. The map will open in your default browser. 

```{r gistmap, eval=FALSE}
mapgist(data=dat, color=c("#976AAE","#6B944D","#BD5945"))
```